A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-11-09 jour/jour.tex
Minor

For \rn{Unique}, Figure~\ref{fig:uniqueness-algo} considers a partition $\mathcal{U}$ of the equivalence classes of our set $\Ec$
such that equivalence classes having a constructor term with top symbol $\const{C}$ are placed in the same subset, for each constructor $\const{C}$.
We write $\ec{t} =_{\mathcal{U}} \ec{u}$ to denote that $\ec{t}$ and $\ec{u}$ reside in the same subset within $\mathcal{U}$.
We then refine $\mathcal{U}$ by 
constructing a partition $\mathcal{U}_i$ of each $U_i \in \mathcal{U}$ such that distinct $\ec{t}$ and $\ec{u}$ reside in the same subset of $\mathcal{U}_i$ 
if and only if they contain constructor terms $\const{C}( t_1, \ldots, t_k )$ and $\const{C}( u_1, \ldots, u_k )$
where each $t_j, u_j$ are such that $\ec{t_j}$ and $\ec{u_j}$ reside in the same subset of $\mathcal{U}$ for each $j=1, \ldots, k$.
Let $\mathcal{U'}$ be the union of each of these partitions.
We update $\mathcal{U}$ to $\mathcal{U'}$.
This refinement is repeated until $\mathcal{U}$ is left unchanged.
If the resulting partition $\mathcal{U}$ contains a subset $U$ having two distinct equivalence classes $\ec{t}$ and $\ec{u}$, then \rn{Unique} applies to $t$ and $u$.

>>>>

For \rn{Unique}, Figure~\ref{fig:uniqueness-algo} considers a partition $\mathcal{U}$ of the equivalence classes of our set $\Ec$
such that codatatype equivalence classes having a constructor term with top symbol $\const{C}$ are placed in the same subset, 
for each constructor $\const{C}$.
We write $\ec{t} =_{\mathcal{U}} \ec{u}$ to denote that $\ec{t}$ and $\ec{u}$ reside in the same subset within $\mathcal{U}$.
We then refine $\mathcal{U}$ by 
constructing a partition $\mathcal{U}_i$ of each $U_i \in \mathcal{U}$ such that distinct $\ec{t}$ and $\ec{u}$ reside in the same subset of $\mathcal{U}_i$ 
if and only if they contain constructor terms $\const{C}( t_1, \ldots, t_k )$ and $\const{C}( u_1, \ldots, u_k )$
where each $t_j, u_j$ are such that $\ec{t_j}$ and $\ec{u_j}$ reside in the same subset of $\mathcal{U}$ for each $j=1, \ldots, k$.
Let $\mathcal{U'}$ be the union of each of these partitions.
We update $\mathcal{U}$ to $\mathcal{U'}$.
This refinement is repeated until $\mathcal{U}$ is left unchanged.
If the resulting partition $\mathcal{U}$ contains a subset $U$ having two distinct equivalence classes $\ec{t}$ and $\ec{u}$, then \rn{Unique} applies to $t$ and $u$.
